Ground state energy of quantum dots using the coupled cluster method

### 2018-06-05 project_2/article/article.tex
Begun implementation section.

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}
\usepackage{simpler-wick}

@@

@@

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}
\usepackage{simpler-wick}
% Code listings
\usepackage{listings, lstautogobble}
% Colors
\usepackage{xcolor}

@@

% Defining color
\definecolor{light-gray}{gray}{0.9}

% Bash language specifier
\lstnewenvironment{bash}
{\lstset{
    basicstyle=\small\ttfamily, language=bash, keywordstyle=\color{blue},
    backgroundcolor=\color{light-gray}, showstringspaces=false,
    frame=single, autogobble=true, morekeywords={make, git}}}
{}

@@

   \section{Implmentation}
        We have costructed a flexible framework for making performing CCD computations,
        consisting of package for python that is easy to install globally on any 
        computer.

        \subsection{Installation}
        The software is easy to install by first cloning the GitHub reopsitory,
        \begin{bash}
            git clone git@github.com:Schoyen/FYS4411.git
        \end{bash}
        Then all you need to do is change directory to the project code folder
        where a \lstinline{MakeFile} is included so you only need to build and
        install,
        \begin{bash}
            cd FYS4411/project_2/coupled-cluster
            make build
            make install
        \end{bash}
